Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/haskellListings.tex
update graph api/update figure
ugh colors..

	basicstyle=\codesize\ttfamily,

@@

	morecomment=[l][\color{gray_ulisses}\ttfamily\codesize]{--},
	morecomment=[s][\color{gray_ulisses}\ttfamily\codesize]{\{-}{-\}},

@@

@@

								genArgs, genWitness, close, witness, mkApps, mkLets, isStuck

@@

                StackSet,NoDuplicates,Data,RBTree,XMonad,Generic,true

@@

		PS,Tip,Node,Black,Red,EQ,False,GT,Just,LT,Left,Nothing,Right,True,Show,Eq,Ord,Num,C,N,Leaf,Bin,CounterExample

>>>>

	basicstyle=\footnotesize\ttfamily,

@@

	morecomment=[l][\color{gray_ulisses}\ttfamily\footnotesize]{--},
	morecomment=[s][\color{gray_ulisses}\ttfamily\footnotesize]{\{-}{-\}},

@@

        escapeinside={(*}{*)},%

@@

                genArgs,genWitness,close,witness,mkApps,mkLets,isStuck,findExpr,updState,putBefore,putAfter,
                putRoot,getNext,getPrev,getSubterms,applyCtx,findApp,findVal,replicate,loop,fac,incAllByOne,map

@@

                StackSet,NoDuplicates,Data,RBTree,XMonad,Generic,
                VState,Expr,Ctx,Cmd,int,list,string,bool

@@

		PS,Tip,Node,Black,Red,EQ,False,GT,Just,LT,Left,Nothing,Right,True,Show,Eq,Ord,Num,C,N,Leaf,Bin,CounterExample,
                StepForward,StepBack,JumpForward,JumpBack,StepOver,StepInto,true
